---
title: "Data Notes & Top‑5 AI Counties"
format:
  html:
    theme: cosmo
execute:
  echo: false
  warning: false
  message: false
---


Slope County, North Dakota is by far the state’s least populous county, with just about 795 residents as of the 2023 American Community Survey five‑year estimate.

Santa Clara County, CA
Often thought of as the heart of Silicon Valley, Santa Clara County has roughly 1.94 million residents and an average AI job share of about 9.7%—nearly six times the national median. Its mature tech ecosystem, home to giants like Apple and Google, helps explain why AI skills are so heavily in demand here.

Fairfax County, VA
Just outside Washington, D.C., Fairfax County is another established innovation hub, with about 1.15 million people and an average AI share of 9.0%. A concentration of government contractors and federal research labs drives strong demand for AI and machine‑learning expertise

Hughes County, SD
By contrast, Hughes County is very rural—home to only around 17,500 people—yet it ranks fourth with an average AI share of 8.4%. This surprising result likely reflects the rise of remote‑friendly roles: even counties far from established tech centers can participate in AI work if infrastructure and broadband allow.

Hudson County, NJ
With roughly 710,000 residents packed into just 46 sq mi, Hudson County (across the river from Manhattan) sees an average AI share of 7.7%. Its dense, transit‑rich urban environment—anchored by Jersey City—supports a booming fintech and data‑services sector that increasingly relies on AI. 



```{r}
# packages
library(tidyverse)
library(readr)
library(kableExtra)
library(tigris)
library(sf)
options(tigris_use_cache = TRUE)

```

```{r}
# 1) Load data
df <- read_csv("data.csv", show_col_types = FALSE)

# 2) Compute per‐county averages for 2018–2023
county_summary <- df %>%
  filter(Year %in% 2018:2023) %>%
  group_by(COUNTY_FIPS) %>%
  summarise(
    avg_ai_share = mean(ai / nads, na.rm = TRUE) * 100,
    avg_pop      = mean(pop,    na.rm = TRUE),
    .groups = "drop"
  )

# 3) Filter to counties with average pop > 50 000 and take top 5 by AI share
top5 <- county_summary %>%
  filter(avg_pop > 50000) %>%
  arrange(desc(avg_ai_share)) %>%
  slice_head(n = 5) %>%
  mutate(Rank = row_number())

# 4) Pull county & state names from TIGER
counties_meta <- counties(cb = TRUE, year = 2020, class = "sf") %>%
  st_drop_geometry() %>%
  transmute(
    COUNTY_FIPS = GEOID,
    County      = NAME,
    state_fips  = STATEFP
  )
states_meta <- states(cb = TRUE, year = 2020, class = "sf") %>%
  st_drop_geometry() %>%
  transmute(
    state_fips = STATEFP,
    State      = STUSPS
  )

# 5) Join and label
top5_named <- top5 %>%
  mutate(COUNTY_FIPS = str_pad(as.character(COUNTY_FIPS), 5, pad = "0")) %>%
  left_join(counties_meta, by = "COUNTY_FIPS") %>%
  left_join(states_meta,   by = "state_fips") %>%
  mutate(County = paste0(County, " County, ", State)) %>%
  select(Rank, County, avg_pop, avg_ai_share)

```

```{r}
top5_named %>%
  transmute(
    Rank,
    County,
    `Avg. Population` = scales::comma(avg_pop),
    `Avg. AI Share (%)` = sprintf("%.2f", avg_ai_share)
  ) %>%
  kable(
    format = "html",
    col.names = c("Rank", "County, State", "Avg. Population", "Avg. AI Share (%)"),
    align = "c"
  ) %>%
  kable_styling(full_width = FALSE, position = "center")

```